% !TeX root = Thesis.tex
\chapter{Main Matter}\label{ch:main-matter}


\section{Construction of the Origami Robot}\label{sec:construction-of-the-origami-robot}

The authors identified precision to be the main challenge for continuum robot arms in related work\cite{santoso_origami_2021}.
They claim that missing torsional twist-resistance is one of the key causes for this precision loss.
Therefore, designing the robot, they focused on a construction with inherent passive torsional twist-resistance.
For this, an origami construction was chosen.
Origami constructions come with the advantage that they can be created by hand from sheets of readily-available materials like paper or plastic which makes their production low-cost.
At the same time they are lightweight and compliant to a degree that can be adjusted by the folding technique used.
This approach for designing soft robots is not new, an overview of previous works can be found in\cite{rus_design_2018}, as the authors point out\cite{santoso_origami_2021}.

For the body, the authors designed a custom modification of the ``Yoshimura'' origami pattern.
A laser-cutter was used to cut the required shapes out of a\ \ac{pet} film, while perforating the lines along which the film was to be folded later.
The origami-tube is assembled by hand and connected to two end-plates, one of which contains a custom-build\ \ac{pcb} that receives instructions from the previous module (or the PC) and executes them, while also passing them on to the next module via wires that run through the center of the origami tube.
The end-plate of one module can be secured to the\ \ac{pcb} of the next, which also transfers power and data via the aforementioned wires.
On top of each\ \ac{pcb} sit three small electric motors which actuate cables that run through the walls of the origami tube and are secured to the end-plate.
It by pulling on these cables, that the segments of the arm can be bent in any direction.
For an even more in-depth look into the construction of the modules, the authors refer to the preceding work\cite{santoso_design_2017}.

The resulting construction is a modular robot arm capable of changing its length to 125\% its contracted length. % todo checken ob
Since each module can bend in any direction, the composed robot arm is capable of complex motion, as the authors demonstrate later in their paper (see\ todo). %todo
The authors measured the torsional stiffness to be about 73 times higher than in a similar soft robot made of silicone, which they call remarkable for its low mass.
Furthermore, they executed a stress-test on the origami-construction, which involved repeated compression and decompression.
After 1000 cycles they observed a maximum reduction in the axial stiffness of $3.14\%$, from which they concluded ``that no significant degradation due to plastic deformation is present''\cite{santoso_origami_2021}.
Even though this reduction might indeed be insignificant for testing the robot in a lab environment without problems, the same might not be true for a real-world application, in which the robot might experience for more than 1000 cycles of (de)compression.
The authors did, however, not mention any additional research concerning the long-term deployment of the used material and origami-structure, which might be a research gap for future work.


\section{Kinematics}\label{sec:kinematics}

The authors describe the inverse kinematics solution for continuum robots to be very complex because of the ``highly nonlinear nature of hyper-redundant continuum robots''\cite{santoso_origami_2021}.
Because of this, they claim that there is ``no closed-form solution for the inverse kinematics of a multi-section continuum robot''\cite{santoso_origami_2021}.
They build on previously conducted research on the topic\cite{neppalli_closed-form_2009,george_thuruthel_learning_2016,lakhal_inverse_2014,singh_performances_2017}, improving and combining different approaches to create an inverse kinematics solver using a damped least-squares jacobian.

Refering to\cite{godage_modal_2015}, for the forward kinematics, they calculated the arc length, bending angle and direction from the tendon lengths, which could then yield the end-plate position for the given segment.
However, as\cite{godage_modal_2015} remarks as well, computing a Jacobian matrix via partial derivatives from this approach is very computationally intense.
Instead, still following\cite{godage_modal_2015}, the authors of the paper used a $10$th-degree Taylor Series for the derivatives.
Having solved the forward-kinematics problem like this, the authors used a damped least-squares Jacobian to iteratively solve the inverse-kinematics problem.

Because of the highly redundant nature of the continuum robot arm, there are many possible solutions, aka tendon lengths, to achieve a desired tip position.
However, many factors apart from the final tip position are to be considered when controlling any robot.
Therefore, the authors proposed three different cost functions.
These cost functions were used as additional criteria to find best of the applicable solutions.

\begin{enumerate}
    \item pose error
    \item module curvature
    \item change in tendon cable lengths
\end{enumerate}

After an in-depth analysis, measuring the computational speed and motion-smoothness of each cost function, the authors concluded that cost function $3$ was best suited, because it yielded by far the smoothest results while being just insignificantly slower to compute than 2.


\section{Feedback Control}\label{sec:feedback-control}

Because the mathematical model of a robot is never perfect, and this is especially true for a soft-robot whose pose is significantly affected by a hand-assembled origami structure, a feedback-control mechanism was deemed to be imperative by the authors\cite{santoso_origami_2021}.
For this, they used an external OptiTrack\footnote{\href{https://optitrack.com}{https://optitrack.com}} system.
This system tracks the position of small infra-red reflectors on the robot using specialized infra-red cameras that are mounted at fixed, known positions around the robot.
The authors stress that this solution is only suited for a lab environment and would need to be replaced by an on-board pose tracking system, should the robot ever be deployed in the field.
Until then, however, the presented solution enabled the authors to combine the iterative inverse kinematics approach with the feedback control provided by the tracking solution to ``drive the system to zero error in configuration space''\cite{santoso_origami_2021}.
Furthermore, with this approach ``the robot was able to traverse in a straight line while maintaining the top plate parallel to the ground [\ldots]. The feedback is able to reduce the error about 5-fold for position and 2.5-fold for orientation tracking''\cite{santoso_origami_2021}.


\section{Grow-To-Shape}\label{sec:grow-to-shape}

Because of the cost function used (minimize change in tendon lengths), the robot is already expected to avoid drastic changes in position if not necessary.
However, to deploy a robot of this kind in an area like minimal-invasive surgeries, as suggested by the authors\cite{santoso_origami_2021}, such changes in position would need to be minimized.
The ``grow-to-shape'' algorithm presented in the paper might be a solution to this challenge.
It uses the length-changing capabilities of the presented robot to let it extend along a given path.
To achieve this, each module is discretized into $10$ points, whose deviation from corresponding points on the desired path is then used as an error function in the inverse kinematics computation.
This approach was tested by the authors in the paper and yielded satisfying results.
One could imagine it being used to transport a surgical tool-tip or camera to a specific location in an organism, while avoiding blood vessels or organs.
